How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
M

Similar statistical analysis is performed on the tortuosity measurements and shown in Fig.~\ref{fig6}(a)--(b). Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$. Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Fig.~\ref{fig6}(c). For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation. As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figs.~\ref{fig6}(d)--(e)

Figures~\ref{fig6}(d)--(e) show that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.

>>>>

Similar statistical analysis is performed on the tortuosity measurements and shown in Fig.~\ref{fig6}(a)--(b). Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$. Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$, however, show similar behavior across different values of $M$, as seen in Fig.~\ref{fig6}(c). For nearly all runs, the tortuosity ratio increases as bodies erode up to a maximum of roughly $(T_2 -1)/(T_1 -1) = 8$, and then the tortuosity ratio decreases near the very end of the simulation. As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figs.~\ref{fig6}(d)--(e). The figure shows that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.
